Figures

### 2020-04-13 manuscript/appendix.Rmd
use GIS-derived intead of map-derived

```{r metric_correlations, fig.cap = "Pearson correlation coefficients of map-derived metrics against inlake slope and deepest point distance metrics.", warning=FALSE, echo = FALSE, eval=FALSE, out.width="11cm", fig.align='center', out.extra=''}
knitr::include_graphics("../figures/metric_correlations-1.pdf")
```

>>>>

```{r metric_correlations, fig.cap = "Pearson correlation coefficients of GIS-derived metrics against inlake slope and deepest point distance metrics.", warning=FALSE, echo = FALSE, eval=FALSE, out.width="11cm", fig.align='center', out.extra=''}
knitr::include_graphics("../figures/metric_correlations-1.pdf")
```
